Response Letter for manuscript TSG-01885-2017 ``Online EV Scheduling Algorithms for Adaptive Charging Networks with Global Peak Constraints'' \\ \vspace{4mm} \large by Bahram~Alinia, Mohammad~H.~Hajiesmaili, Zachary J. Lee, Noel Crespi, and Enrique Mallada

### 2019-08-25 TSC/R1/similarResponseLetters/ResponseLetter-tsg-submitMay11.tex

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newpage
\section{Reviewer $\# 3$}
{\color{blue}}
%
%\vspace{4mm}
%{\color{blue}\noindent\\
%We sincerely appreciate you for taking the time to review
%our paper. Following the concerns and suggestions, the paper
%has carefully been revised to address the reviewer's comments
%properly.
%}

{\color{blue}The authors of the paper, "Online ev scheduling algorithms for adaptive charging networks with global peak constraints", proposed online scheduling approaches of electric vehicles considering the peak constraints in the multi-layer charging networks, and integers constraints of the decision variables. This paper presents interesting research ideas of approximating the MILP problem with bounds. However, the reviewer has the following concerns that need to be addressed:}

\subsection{Comments}
%We sincerely appreciate you for taking the time to review our paper. Following the
%concerns and suggestions, the paper has carefully been revised to address the reviewer's
%comments properly.

\vspace{5mm}
{
{\color{blue}\noindent\textbf{Comment 3.1:}\\
Most of the previous optimization-based EV scheduling algorithms, the demand is treated as a constraint, i.e. the charging system has to deliver the demand before the vehicle leaves. In this paper, this constraint does not have to be satisfied. Please provide justifications. In addition, the scenario with the peak constraints from system operators also needs to be justified. It's better to associate the problem setting with real-world markets. For instance, in California, TOU pricing with energy charge and demand charge (cost applied to monthly global peaks) can be integrated. A sample paper minimizing demand charges instead of modeling it as an imaginative constraint can be found:
J. Jin and Y. Xu, "Optimal Storage Operation Under Demand Charge," in IEEE Transactions on Power Systems, vol. 32, no. 1, pp. 795-808, Jan. 2017.
}}

\vspace{5mm}
\noindent\textbf{Response:}

Thanks for this constructive comment. We justified our particular scenario as compared to the scenarios with demand as a constraint in the second paragraph of the Introduction (see highlighted section in the revised paper). As pointed by the reviewer the scenarios with demand as a constraints accounts for the low-load regimes where there is no limit on the resources (capacity of the charging networks). This scenario mainly captures the current EV charging scheduling models, where the number of EVs are not too large.

In contrast, our study tackles the high-load regimes which is motivated by the rapid proliferation of EV usage as supported by providing some stats regarding global EV usage in the first paragraph of the Introduction. In high-load regime, the aggregate EV demands are beyond the capacity of charging network (due to physical limitations of transformers or several other issues enforced by station operator. Please see Section I, third paragraph, the last sentence as highlighted). This argument also justifies the peak constraints from system operators as well.

Associating the problem to the real-world electricity market is a very fascinating future research direction, where the charging station operator can participate in market and buy the electricity demand of EVs directly from the market using TOU pricing model. Our preliminarily investigation shows that the underlying optimization problem is fundamentally different than our focus in this work and we plan to tackle this scenario as a future study. Last, we appreciate the provided reference by the reviewer and mentioned this future direction in our related work section, with citing the suggested paper. For details, please see Section II, Page 2, last paragraph.   And also the last sentence in Conclusion.

\vspace{5mm}
{
{\color{blue}\noindent\textbf{Comment 3.2:}\\
In the charging network, what standards are these charging stations complying with? Are they level I, Level II, or DC fast chargers? The charging power usually depends on the chargers instead of the vehicle types. Thus, the max charging rates in table III are not valid. If they are level II with SAE J1772 protocol, there is another constraint that the power cannot be controlled continuously, i.e the controllable power range is {0} U [1.5 6.6kW]. Thus, another integer is needed to model this property.
}}

\vspace{5mm}
\noindent\textbf{Response:}

In the revised manuscript, we changed the simulation setting according to this comment and re-run all the simulations. In the new setting, the charging speed of the EVs depends on the installed DC chargers in the stations. It is assumed that the chargers use CHAdeMO charging method and can provide a charging rate up to 50 kW. Moreover, regarding controlling the charging rates, we assumed in the paper that the charging rate of an EV is fixed during a time slot, which is a common assumption in time slot-based system models in EV (or job) scheduling domain (e.g., see [8], [11], [33] in the revised manuscript).  Therefore, charging rates do not change too frequently but only in the beginning of each time slot. It is worth to note that in our algorithm design, most of the times the charging rates are set to the maximum values, in this way, we do not expect too much fluctuations in charging scheduling of each EV.

\vspace{5mm}
{
{\color{blue}\noindent\textbf{Comment 3.3:}\\
 Following the modeling in this paper, it seems the uncertainties of future arrival vehicles are not modeled. A similar charging station with multiple outlets can be found in:
B. Wang, Y. Wang, H. Nazaripouya, C. Qiu, C. C. Chu and R. Gadh, "Predictive Scheduling Framework for Electric Vehicles With Uncertainties of User Behaviors," in IEEE Internet of Things Journal, vol. 4, no. 1, pp. 52-63, Feb. 2017.
Bin Wang et al., "Predictive scheduling for Electric Vehicles considering uncertainty of load and user behaviors," 2016 IEEE/PES Transmission and Distribution Conference and Exposition (T\&D), Dallas, TX, 2016, pp. 1-5.
But impact of future demands from EVs is significant and needs proper treatment. So please justify the advantages of not modeling these uncertainties. In addition, there are MPC based approaches to handling these uncertainties:
N. Chen, L. Gan, S. H. Low, and A. Wierman, "Distributional analysis for model predictive deferrable load control," in 2014 IEEE 53rd Annual Conference on Decision and Control (CDC), 2014, pp. 6433-6438
}}

\vspace{5mm}
\noindent\textbf{Response:}

In Related Work (Page 2 of the revised manuscript), we added a paragraph to compare our approach and prediction-based approaches. We have mentioned that the prediction-based approaches achieve satisfactory performance for the scenarios that follow prediction. Deviation from prediction models, however, degrades their performance. Our approach, on the other hand, has no assumptions on modeling/prediction, and in this way, is robust against any uncertainty in the instances to the problem.

On top of the above argument we would like to further highlight that in several cases, studies that apply prediction-based approaches usually rely on unrealistic assumptions which may not reflect real world scenarios accurately. 
Our algorithms are very simple and easy to implement. And as supported by the trace-driven experiments, the proposed algorithms can achieve satisfactory performance as compared to the optimal solutions, where all the uncertain inputs are given in advance. 
\\

\vspace{5mm}
{
{\color{blue}\noindent\textbf{Comment 3.4:}\\
What is computational complexity of the MILP problem in this paper? Please provide more info about the experiments, e.g. memory size, number of cores, etc. There are emerging parallel algorithms to handle binary/integer variables in MILP problem using multi-core computers. The reviewer is wondering why the problem cannot be solved by existing parallel solutions with multi-core computers and what the advantages of the proposed approaches in this paper.
}}

\vspace{5mm}
\noindent\textbf{Response:}

The underlying MILP problem is an NP-hard problem since it is a time expanded version of integer knapsack problem, so, it is computationally infeasible to solve optimally. 
Our proposed algorithms, however, are ``sub-optimal'' approximate or competitive algorithms with performance guarantees against optimum (see Theorems 3, 4, and 5). We analyzed the computational complexities of our algorithms and the summary of them is listed in Table II. In short, all of them are polynomial algorithms that could be implemented fast.

We would like to emphasize that we study ``online scenarios'' for the LP and MILP problems in the paper, and since the input to the problems are not available fully in advance, we cannot solve them by the commercial solvers. Consequently, the main challenge here is not the computational complexity of the algorithm, but the efficiency of the algorithm in the absence of future demands.

%Thanks for this useful comment.

%We thank the reviewer for pointing this out.

%Thanks for suggesting this point.

%We acknowledge the reviewer for suggesting this point. We agree that the

%We sincerely appreciate you for taking the time to review our paper. Following the concerns and suggestions, the paper has carefully been revised to address the reviewer's comments properly. We also tried to briefly reflect all the clarifications in the revised 4-page manuscript.

%Thanks. We agree that .....

%We agree that ....

%We thank the reviewer for pointing this out.

%Thanks for highlighting this point.

%We thank the reviewer for pointing this precious comment.

%Thanks for pointing this issue.

%We thank the reviewer for suggesting this point.

%\begin{itemize}
%\item[[A7]] D. G. Luenberger, Optimization by Vector Space Methods, John Wiley and Sons, Inc., New York, 1969.   
%\end{itemize}

%\vspace{5mm}
%\noindent\textbf{Response:}\\
%Thanks. We believe that the response to this comment is given within our response to Comment 3.11 above.

%\item In TCOMMIT, Lines 6-8 of SetGamma should be replaced

\bibliography{ref-response}{}
\vspace{-3mm}
\bibliographystyle{ieeetr}

\end{document}

6741 460 573 918
